A Hitchhiker's Guide to Reproducible Research in R

### 2021-07-05 manuscript.Rmd
dont use pipe in example

```{r}
set.seed(112358) # fix state of RNG
simulate_data(n = 400, # n/2 per group
              df = 8, # Chisq with skewness == 1
              d = .2, # Cohen's D
              i = 10) %>% # number of items (should not effect outcome)
  planned_analysis() %>% # `%>%` = output of 1. function becomes argument 2.
  .$test %>% # extract the t.test object
  report::report_text() # use the `report`-package
```

>>>>

```{r}
set.seed(112358) # fix state of RNG
report::report_text(
  planned_analysis(
    simulate_data(
      n = 400,# Sample size
      df = 8, # Chisq with DF = 8 has skewness = 1
      d = .2, # Cohen's D
      i = 10  # Number of items (should not effect anything)
    )
  )$test
)
```
